\section{Lessons learned perspective} \label{section:Lessons learned perspective}
\subsection{Issues: evolution and refactoring}
Initially, the inherited code was translated to a basic Java application using the Java Spark framework\footnote{\url{https://github.com/DevOps2021-gb/devops2021/issues/152}}. At the time, this code was very bare-bones with all logic and endpoints located in a single file. As time went on, the team refactored the application to make use of a more well structured system architecture (controller-, service-, persistance-layer)\footnote{\url{https://github.com/DevOps2021-gb/devops2021/tree/ae6cd48a06fde2a5c403056b33895b7589cb039d}} eventually adding dependency injection and mock testing\footnote{\url{https://github.com/DevOps2021-gb/devops2021/commit/07914442a09e204f0be2687fe8e5b9bd07799ee4}} to the application. 
During development one of the endpoint's response codes was changed which led to a massive increase in errors the simulator reported, which could have been avoided if a fraction of the provided \texttt{minitwit\_simulator.py} file had been a part of the test pipeline.

\subsection{Issues: operation}
\label{issues-operation}
The self-made heartbeat protocol had some issues related to Spark. An issue\footnote{\url{https://github.com/DevOps2021-gb/devops2021/issues/171}} was created trying to remedy this but was never finished, rendering the availability part of the system unstable as the backup would perceive the primary to be down and then reassign the floating-ip to itself exposing a single point of failure. The issue is likely related to Spark's session handling.\\

Early on in the project the database was deployed together with the Minitwit application using Vagrant. Due to SSH key mismanagement, we lost access to our vagrant deployed DigitalOcean Minitwit server containing simulator generated data. Luckily, we were able to reset the root user through Digital Ocean's web terminal functionality. Through this terminal we could add SSH public keys to the \textit{authorized\_keys} file. Finally, we could then SSH into the server and get a database dump. This database dump was based on an outdated model with no ORM, so we had to alter the tables before transferring it to the new remote database server. Only a minor amount of data was lost during the data transfer. To minimize data loss in the future we created a backup GitHub Action that made a database backup once a day. In addition, SSH keys for the server were backed up in a keystore.

On the 18th of March the webserver crashed due to SSL exceptions. After looking through Docker logs, we narrowed it down to an incompatibility between java-mysql-connector 8.0.15 and Java 11. The solution to this was to update java-mysql-connector 8.0.15 to 8.0.23 \footnote{\url{https://github.com/DevOps2021-gb/devops2021/issues/94}}.
\todo{no automatic versioning - ved ikke om det er nemt specifikt for java 11}

\subsection{Issues: maintenance}
\label{issues-maintenance}
The group never figured out how to make SonarCloud read the test coverage\footnote{\url{https://github.com/DevOps2021-gb/devops2021/issues/140}}, eventually scrapping the idea after spending much time trying to make it work. It should however be said that it is able to identify which test functions are proper test functions and that code coverage is obtainable through an IDE like IntelliJ.

Furthermore, the group tried to implement alert notifications on Grafana\footnote{\url{https://github.com/DevOps2021-gb/devops2021/issues/87}} in order to be notified of unexpected data from the monitoring but this was never successfully implemented.